\vspace{-2.0cm}Stuff

### 2014-06-03 report/draft3.tex
Modified equations

\usepackage{fullpage}
\usepackage{floatrow}
\usepackage{fourier}
\usepackage{parskip}% http://ctan.org/pkg/parskip
\usepackage{graphicx}
\usepackage[labelfont={bf},margin=1cm]{caption}
\usepackage{subcaption}
\usepackage{textcomp}
%\usepackage[round,authoryear]{natbib}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber,citestyle=authoryear,bibstyle=authoryear,maxbibnames=10]{biblatex}
\addbibresource{VCPbibliography.bib}

@@

\begin{document}
%Ignore this page, it's so I can have a reference for the different citation formats and will be removed before turning in the paper.
%
%
%cite \cite{buckland2001} \cite{komodo2013} \\
%cite* \cite*{buckland2001} \cite*{komodo2013}\\
%parencite \parencite{buckland2001} \parencite{komodo2013}\\
%parencite* \parencite*{buckland2001} \parencite*{komodo2013}\\
%textcite \textcite{buckland2001} \textcite{komodo2013}\\
%smartcite - does the super script/foot note thing.
%\newpage
\begingroup  
  \centering
  \LARGE Masters Report - Variable Circular Plots: Station Placement and the Independence Assumption\\[1em]
  \large Matt Edwards\\
  26 May 2014\par
\endgroup

@@

$\hat{D}=n/(Area)*P(observing object|distance r)$

@@

$\theta = \frac{\sqrt{\pi /2}}{\sigma}$

@@

$\sigma = w/3.5 = 0.1429$

$\theta = \frac{\sqrt{\pi /2}}{0.1429}=8.7732$

For a half-normal with parameter $\theta=8.7732$, $f(0)=5.5852$ so to scale the value to 1:
\begin{center}
$\delta_{HN} = 1/5.5852 = 0.1790$
\end{center}

Half-normal density functions were executed in R with the \texttt{fdrtool} package.

\subsubsection{Empirical Observations}
\begin{figure}
	\includegraphics[width=\textwidth]{../images/loess.pdf}
	\caption{Empirical Observation Distances from Original data in meters, with LOESS regression lines. Bin width=5 m\label{fig:by5}}
\end{figure}

We can see in Figure \ref{fig:by5} that above 100 m, observations were commonly heaped into 10 or 25 m distances, with the latter being more heavily used. Above 200 m, 50 m heaps were common.

@@

$\delta_{EMP}=\frac{1}{max(predicted)}=40.5780$

@@

$E[observed] = Area*Density*P(object observed | distance r)$

>>>>

\usepackage{fullpage}
\usepackage{floatrow}
\usepackage{fourier}
\usepackage{parskip}% http://ctan.org/pkg/parskip
\usepackage{graphicx}
\usepackage[labelfont={bf},margin=1cm]{caption}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{amsmath} %larger fractions
%\usepackage[round,authoryear]{natbib}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber,citestyle=authoryear,bibstyle=authoryear,maxbibnames=10]{biblatex}
\addbibresource{VCPbibliography.bib}

@@

\begin{document}
%Ignore this page, it's so I can have a reference for the different citation formats and will be removed before turning in the paper.
%
%
%cite \cite{buckland2001} \cite{komodo2013} \\
%cite* \cite*{buckland2001} \cite*{komodo2013}\\
%parencite \parencite{buckland2001} \parencite{komodo2013}\\
%parencite* \parencite*{buckland2001} \parencite*{komodo2013}\\
%textcite \textcite{buckland2001} \textcite{komodo2013}\\
%smartcite - does the super script/foot note thing.
%\newpage
\begingroup  
  \centering
  \LARGE Masters Report - Variable Circular Plots: Station Placement and the Independence Assumption\\[1em]
  \large Matt Edwards\\
 % 26 May 2014\par
  \today\par
\endgroup

@@

$\hat{D}=n/(\mbox{Area})*P(\mbox{observing object}|\mbox{distance }r)$

@@

$\theta = \dfrac{\sqrt{\pi /2}}{\sigma}$

@@

$\sigma = \dfrac{w}{3.5} = 0.1429$

$\theta = \dfrac{\sqrt{\pi /2}}{0.1429}=8.7732$

For a half-normal with parameter $\theta=8.7732$, $f(0)=5.5852$ so to scale the value to 1:
\begin{center}
$\delta_{HN} = \dfrac{1}{5.5852} = 0.1790$
\end{center}

Half-normal density functions were executed in R with the \texttt{fdrtool} package.
\begin{figure}
	\includegraphics[width=\textwidth]{../images/loess.pdf}
	\caption{Empirical Observation Distances from Original data in meters, with LOESS regression lines. Bin width=5 m\label{fig:by5}}
\end{figure}
\subsubsection{Empirical Observations}
Figure \ref{fig:by5} illustrates that above 100 m, observations were commonly heaped into 10 or 25 m distances, with the latter being more heavily used. Above 200 m, 50 m heaps were common.

@@

$\delta_{EMP}=\dfrac{1}{max(predicted)}=40.5780$

@@

$E[observed] = Area*Density*P(\mbox{object observed}|\mbox{distance }r)$
